\chapter{Language bindings}
\minitoc

libsax has been developed as a C++ written library which means
including this library into languages providing an object model
is an easy task. To be able to use the library within languages
providing only support for basic types an interface wrapper has
been included which handles objects as ID's and provides the basic
public constructors and members as simple functions.

\section{SWIG}

SWIG (Simple Wrapper Interface Generator) is a software development tool
that simplifies the task of
interfacing different languages to C and C++ programs. In a nutshell,
SWIG is a compiler that takes C declarations and creates the wrappers
needed to access those declarations from other languages
including:

\begin{itemize}
\item csharp , java
\item perl5 , php4 , python , tcl
\end{itemize}

Concerning our development requirements we can say:

\begin{itemize}
\item In case of well written libraries the process of generating
      language bindings can be automated.
\item typemaps for transforming the C++ types used within the library
      must be provided for each destination language.
\item STL written libraries can make use of the typemaps already
      provided by swig
\end{itemize}

\newpage

\section{Interface file for libsax (SaX.i)}

\begin{Command}{12cm}
\begin{small}
\begin{verbatim}
//==================================
// Interface definition for libsax
//----------------------------------
#define NO_OPERATOR_SUPPORT 1
%module SaX
%{
#include "../sax.h"
%}
//==================================
// SWIG includes
//----------------------------------
%include exception.i

//==================================
// Typemaps
//----------------------------------
//==================================
// Allow QString return types
//----------------------------------
// [ destination language dependant ]
// ...

//==================================
// Allow QString refs as parameters
//----------------------------------
// [ destination language dependant ]
// ...

//==================================
// Allow QDict<QString> return types
//----------------------------------
// [ destination language dependant ]
// ...

//==================================
// Allow QList<QString> return types
//----------------------------------
// [ destination language dependant ]
// ...

\end{verbatim}
\end{small}
\end{Command}

\newpage

\begin{Command}{12cm}
\begin{small}
\begin{verbatim}
//==================================
// Exception class wrapper...
//----------------------------------
class SaXException {
    public:
    int   errorCode          ( void );
    bool  havePrivileges     ( void );
    void  errorReset         ( void );

    public:
    QString errorString  ( void );
    QString errorValue   ( void );

    public:
    void setDebug ( bool = true );
};
//==================================
// ANSI C/C++ declarations...
//----------------------------------
%include "../storage.h"
%include "../process.h"
%include "../export.h"
%include "../import.h"
%include "../init.h"
%include "../config.h"
%include "../card.h"
%include "../keyboard.h"
%include "../pointers.h"
%include "../desktop.h"
%include "../extensions.h"
%include "../layout.h"
%include "../path.h"
%include "../sax.h"
\end{verbatim}
\end{small}
\end{Command}

\newpage

\subsection{Interface explanations}
The interface file is divided into four \textit{sections} which
handles the following interfacing problems:

\begin{enumerate}
\item Module name and include files to be able to create the
      wrapper code. The namespace used here is called \textbf{SaX}
\item type mappings from C++ into the destination language.
      Currently perl,python,java and csharp types are supported.
\item Exception class wrapper which doesn't include the Qt signal/slot
      definitions
\item Declarations used to create an interface for the destination
      language. Refering to perl this information is used to create
      the appropriate SaX.pm file
\end{enumerate}

\section{Example: libsax used with perl...}
The following examples will do the same as the last example from the
Examples chapter; Changing the default colordepth of the current
configuration to 24 bit.

\begin{Command}{12cm}
\begin{small}
\begin{verbatim}
use SaX;
sub main {
    my %section;
    my @importID = (
        $SaX::SAX_CARD, $SaX::SAX_DESKTOP, $SaX::SAX_PATH
    );
    my $config = new SaX::SaXConfig;
    foreach my $id (@importID) {
        $import = new SaX::SaXImport ( $id );
        $import -> setSource ( $SaX::SAX_SYSTEM_CONFIG );
        $import -> doImport();
        $config -> addImport ( $import );
        $section{$import->getSectionName()} = $import;
    }
    my $mDesktop = new SaX::SaXManipulateDesktop (
        $section{Desktop},$section{Card},$section{Path}
    );
    if ($mDesktop->selectDesktop (0)) {
        $mDesktop->setColorDepth (24);
    }
    $config -> setMode (SaX::SAX_MERGE);
    $config -> createConfiguration();
}
main();
\end{verbatim}
\end{small}
\end{Command}
